Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-17 report/report.tex
Add note about GIS quality, biljecki

This project assesses the feasibility of reconstructing a city from OpenStreetMap (OSM) road and building data, and will focus on the feasibility of including pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.

@@

>>>>

Currently, when modeling
3D GIS datasets without errors are rare. While previously \textbf{(Biljecki et al, 2016)} note that there are coming more and more sophisticated methods for automatically correcting the most common errors.
Among the most common errors: Missing or invalid geometry, invalid semantics.
GIS validation har only been a topis of research lately, and many such datasets were usually obtained years ago, and creating error-free datasets was neither possible due to the lack of validation techniques, nor a high priority.

The idea of gathering geodata from OpenStreetMap (OSM), where the temporal aspect of data accuracy is perhaps mitigated by the crowd contribution nature.
There have already been a few services (*** Name a few services + links)
but such services are usually limited in the type of data that they can provide. Usually they focus on obtaining either road networks or buildings separately, and in the case of road networks they usually focus on car road networks (why? Driving games?***), and roads designated for energy efficient mobility are left out.

This project assesses the feasibility of reconstructing a city from OSM road and building data, and will focus on the feasibility of including pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.

@@

\bibitem{biljecki-16}
%TODO
Biljecki, F
2016
THE MOST COMMON GEOMETRIC AND SEMANTIC ERRORS IN CITYGML DATASETS
